
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library('papaja')

df_results <- readRDS('final_results.rds')

# Mean
mean_savage_dickey_bf <- mean(df_results$savage_dickey_bf)
mean_directional_bf <- mean(df_results$directional_bf)
mean_p_effect <- mean(df_results$p_effect)

# SD
sd_savage_dickey_bf <- sd(df_results$savage_dickey_bf)
sd_directional_bf <- sd(df_results$directional_bf)
sd_p_effect <- sd(df_results$p_effect)

# Mean within sample range (mwsr)
get_mean_within_sample_range <- function(column){
  range_vec <- vector()
  for (i in seq(from = 1, by = 8, length.out = length(column)/8)){
    range_vec <- append(range_vec, range(column[seq(i, i+7)]))
  }
  return(mean(range_vec))
}

mwsr_savage_dickey_bf <- get_mean_within_sample_range(df_results$savage_dickey_bf)
mwsr_directional_bf <- get_mean_within_sample_range(df_results$directional_bf)
mwsr_p_effect <- get_mean_within_sample_range(df_results$p_effect)

# False positive results
fp_savage_dickey_bf_3 <- sum(df_results$fp_savage_dickey_bf_3)/nrow(df_results)

fp_directional_bf_3 <- sum(df_results$fp_directional_bf_3_pos,
                           df_results$fp_directional_bf_1_3_neg)/nrow(df_results)

fp_directional_bf_10 <- sum(df_results$fp_directional_bf_10_pos,
                            df_results$fp_directional_bf_1_10_neg)/nrow(df_results)

fp_directional_bf_30 <- sum(df_results$fp_directional_bf_30_pos,
                            df_results$fp_directional_bf_1_30_neg)/nrow(df_results)

fp_directional_bf_100 <- sum(df_results$fp_directional_bf_100_pos,
                             df_results$fp_directional_bf_1_100_neg)/nrow(df_results)

fp_p_effect_95 <- sum(df_results$fp_p_effect_95_pos,
                      df_results$fp_p_effect_05_neg)/nrow(df_results)

fp_p_effect_975 <- sum(df_results$fp_p_effect_975_pos,
                       df_results$fp_p_effect_025_neg)/nrow(df_results)

fp_p_effect_99 <- sum(df_results$fp_p_effect_99_pos,
                      df_results$fp_p_effect_01_neg)/nrow(df_results)

fp_hdi_80 <- sum(df_results$fp_hdi_80_pos,
                 df_results$fp_hdi_80_neg)/nrow(df_results)

fp_hdi_90 <- sum(df_results$fp_hdi_90_pos,
                 df_results$fp_hdi_90_neg)/nrow(df_results)

fp_hdi_95 <- sum(df_results$fp_hdi_95_pos,
                 df_results$fp_hdi_95_neg)/nrow(df_results)

fp_hdi_99 <- sum(df_results$fp_hdi_99_pos,
                 df_results$fp_hdi_99_neg)/nrow(df_results)


# Diverging results (first method shows effect, second method not)
dr_savage_dickey_bf_directional_bf <- sum(df_results$fp_savage_dickey_bf_conv == 1 &
                                            df_results$fp_directional_bf_pos_conv == 0 &
                                            df_results$fp_directional_bf_neg_conv == 0)

dr_savage_dickey_bf_hdi <- sum(df_results$fp_savage_dickey_bf_conv == 1 &
                                 df_results$fp_hdi_pos_conv == 0 &
                                 df_results$fp_hdi_neg_conv == 0)

dr_savage_dickey_bf_p_effect <- sum(df_results$fp_savage_dickey_bf_conv == 1 &
                                      df_results$fp_p_effect_pos_conv == 0 &
                                      df_results$fp_p_effect_neg_conv == 0)

dr_directional_bf_savage_dickey_bf <- sum(df_results$fp_directional_bf_pos_conv == 1 &
                                            df_results$fp_savage_dickey_bf_conv == 0,
                                          df_results$fp_directional_bf_neg_conv == 1 &
                                            df_results$fp_savage_dickey_bf_conv == 0)

dr_directional_bf_hdi <- sum(df_results$fp_directional_bf_pos_conv == 1 &
                               df_results$fp_hdi_pos_conv == 0,
                             df_results$fp_directional_bf_neg_conv == 1 &
                               df_results$fp_hdi_neg_conv == 0)

dr_directional_bf_p_effect <- sum(df_results$fp_directional_bf_pos_conv == 1 &
                                    df_results$fp_p_effect_pos_conv == 0,
                                  df_results$fp_directional_bf_neg_conv == 1 &
                                    df_results$fp_p_effect_neg_conv == 0)

dr_hdi_savage_dickey_bf <- sum(df_results$fp_hdi_pos_conv == 1 &
                                 df_results$fp_savage_dickey_bf_conv == 0,
                               df_results$hdi_neg_conv == 1 &
                                 df_results$fp_savage_dickey_bf_conv == 0)

dr_hdi_directional_bf <- sum(df_results$fp_hdi_pos_conv == 1 &
                               df_results$fp_directional_bf_pos_conv == 0,
                             df_results$fp_hdi_neg_conv == 1 &
                               df_results$fp_directional_bf_neg_conv == 0)

dr_hdi_p_effect <- sum(df_results$fp_hdi_pos_conv == 1 &
                         df_results$fp_p_effect_pos_conv == 0,
                       df_results$fp_hdi_neg_conv == 1 &
                         df_results$fp_p_effect_neg_conv == 0)

dr_p_effect_savage_dickey_bf <- sum(df_results$fp_p_effect_pos_conv == 1 &
                                      df_results$fp_savage_dickey_bf_conv == 0,
                                    df_results$hdi_p_effect_neg_conv == 1 &
                                      df_results$fp_savage_dickey_bf_conv == 0)

dr_p_effect_directional_bf <- sum(df_results$fp_p_effect_pos_conv == 1 &
                                    df_results$fp_directional_bf_pos_conv == 0,
                                  df_results$fp_p_effect_neg_conv == 1 &
                                    df_results$fp_directional_bf_neg_conv == 0)

dr_p_effect_hdi <- sum(df_results$fp_p_effect_pos_conv == 1 &
                         df_results$fp_hdi_pos_conv == 0,
                       df_results$fp_p_effect_neg_conv == 1 &
                         df_results$fp_hdi_neg_conv == 0)


# Prior sensitivity (ps; proportion of samples in which a method came to diverging results)
get_ps_null_method <- function(column){
  counter <- 0
  for (i in seq(from = 1, by = 8, length.out = length(column)/8)){
    if (all(column[i] == column[seq(i, i+7)]) == FALSE){
      counter <- counter + 1
    }
  }
  proportion <- counter/(length(column)/8)
  return(proportion)
}


get_ps_directional_method <- function(column_pos, column_neg){
  counter <- 0
  for (i in seq(from = 1, by = 8, length.out = length(column_pos)/8)){
    if ((all(column_pos[i] == column_pos[seq(i, i+7)]) == TRUE) &
        (all(column_neg[i] == column_neg[seq(i, i+7)]) == TRUE)){
      counter <- counter + 1
    }
  }
  proportion <- 1 - counter/(length(column_pos)/8)
  return(proportion)
}


ps_savage_dickey_bf_conv <- 
  get_ps_null_method(df_results$fp_savage_dickey_bf_conv)

ps_savage_dickey_bf_conv_0_2 <-
  get_ps_null_method(df_results$fp_savage_dickey_bf_conv[df_results$s_log_k_sd == 0.2])

ps_savage_dickey_bf_conv_0_51 <- 
  get_ps_null_method(df_results$fp_savage_dickey_bf_conv[df_results$s_log_k_sd == 0.51])

ps_savage_dickey_bf_conv_0_81 <- 
  get_ps_null_method(df_results$fp_savage_dickey_bf_conv[df_results$s_log_k_sd == 0.81])


ps_directional_bf_conv <- 
  get_ps_directional_method(df_results$fp_directional_bf_pos_conv,
                            df_results$fp_directional_bf_neg_conv)

ps_directional_bf_conv_0_2 <- 
  get_ps_directional_method(df_results$fp_directional_bf_pos_conv[df_results$s_log_k_sd == 0.2],
                            df_results$fp_directional_bf_neg_conv[df_results$s_log_k_sd == 0.2])

ps_directional_bf_conv_0_51 <-
  get_ps_directional_method(df_results$fp_directional_bf_pos_conv[df_results$s_log_k_sd == 0.51],
                            df_results$fp_directional_bf_neg_conv[df_results$s_log_k_sd == 0.51])

ps_directional_bf_conv_0_81 <-
  get_ps_directional_method(df_results$fp_directional_bf_pos_conv[df_results$s_log_k_sd == 0.81],
                            df_results$fp_directional_bf_neg_conv[df_results$s_log_k_sd == 0.81])


ps_hdi_conv <- 
  get_ps_directional_method(df_results$fp_hdi_pos_conv,
                            df_results$fp_hdi_neg_conv)

ps_hdi_conv_0_2 <- 
  get_ps_directional_method(df_results$fp_hdi_pos_conv[df_results$s_log_k_sd == 0.2],
                            df_results$fp_hdi_neg_conv[df_results$s_log_k_sd == 0.2])

ps_hdi_conv_0_51 <- 
  get_ps_directional_method(df_results$fp_hdi_pos_conv[df_results$s_log_k_sd == 0.51],
                            df_results$fp_hdi_neg_conv[df_results$s_log_k_sd == 0.51])

ps_hdi_conv_0_81 <- 
  get_ps_directional_method(df_results$fp_hdi_pos_conv[df_results$s_log_k_sd == 0.81],
                            df_results$fp_hdi_neg_conv[df_results$s_log_k_sd == 0.81])


ps_p_effect_conv <- 
  get_ps_directional_method(df_results$fp_p_effect_pos_conv,
                            df_results$fp_p_effect_neg_conv)

ps_p_effect_conv_0_2 <- 
  get_ps_directional_method(df_results$fp_p_effect_pos_conv[df_results$s_log_k_sd == 0.2],
                            df_results$fp_p_effect_neg_conv[df_results$s_log_k_sd == 0.2])

ps_p_effect_conv_0_51 <- 
  get_ps_directional_method(df_results$fp_p_effect_pos_conv[df_results$s_log_k_sd == 0.51],
                            df_results$fp_p_effect_neg_conv[df_results$s_log_k_sd == 0.51])

ps_p_effect_conv_0_81 <- 
  get_ps_directional_method(df_results$fp_p_effect_pos_conv[df_results$s_log_k_sd == 0.81],
                            df_results$fp_p_effect_neg_conv[df_results$s_log_k_sd == 0.81])

```

`\section{Results}`
Within samples, the mean range of Savage-Dickey BFs was `r mwsr_savage_dickey_bf`, the mean range of dBFs was `r mwsr_directional_bf` and the mean range of P(effect > 0) proportions was `r mwsr_p_effect`.`\\`

`\subsection{False positive results}`
With a decision threshold of 3, `r round(fp_savage_dickey_bf_3 * 100, 2)``\%` of Savage-Dickey BFs were false positive. With a decision threshold of 1/3 for a negative and 3 for a positive effect, `r round(fp_directional_bf_3 * 100, 2)``\%` of dBFs were false positive. With 1/10 and 10 as directional decision thresholds, `r round(fp_directional_bf_10 * 100, 2)``\%` of dBFs were false positive, with 1/30 and 30, `r round(fp_directional_bf_30 * 100, 2)``\%` and with 1/100 and 100, `r round(fp_directional_bf_100 * 100, 2)``\%`. With a 80`\%` HDI, `r round(fp_hdi_80 * 100, 2)``\%` of results were false positive, with a 90`\%` HDI, `r round(fp_hdi_90 * 100, 2)``\%`, with a 95`\%` HDI, `r round(fp_hdi_95 * 100, 2)``\%` and with a 99`\%` HDI, `r round(fp_hdi_99 * 100, 2)``\%`. With P(effect > 0) >.95 for a positive and P(effect > 0) <.05 for negative effect, `r round(fp_p_effect_95 * 100, 2)``\%` of results were false positive. With >.975 and <.025 as directional thresholds, `r round(fp_p_effect_975 * 100, 2)``\%` and with >.99 and <.01, `r round(fp_p_effect_99 * 100, 2)``\%` of results were false positive. See Figure `\ref{fig:fig_fp}` for the proportions of false positive results per effect SD.`\\`

`\subsection{Simulation-based decision thresholds}`

`\subsubsection{Multiple tests}`

`\subsubsection{Overlap of false positive results}`

`\subsubsection{Prior sensitivity}`







# **Diverging results**
All models with false positive Savage-Dickey BFs, HDIs or P(effect) proportions were also significant with the dBF (check with new data). `r` of false positive Savage-Dickey BFs were accompanied by a significant HDI and `r` with a significant P(effect > 0). `r` % of significant HDIs were also false positive with P(effect > 0) and `r` with the Savage-Dickey BF. When P(effect > 0) indicated an effect this was also indicated by the Savage-Dickey BF in `r`% of the models and in `r` % of HDIs.

False positive dBFs were accompanied by `r`% of Savage-Dickey BFs

The results of HDI and P(effect > 0) diverged for `r` % of models.

# **Prior sensitivity**
Within `r round(ps_savage_dickey_bf_conv * 100, 2)``\%` of all samples the Savage-Dickey BF came to diverging results due to different priors. The dBF produced inconsistent results within `r round(ps_directional_bf_conv * 100, 2)``\%` of all samples. Different priors produced different results within `r round(ps_hdi_conv * 100, 2)``\%` of all samples with the HDI decision rule and P(effect > 0) came to diverging results within `r round(ps_p_effect_conv * 100, 2)``\%` of all samples. See Table `\ref{tab:prior_sensitivity}` for the prior sensitivities per effect SD.`\\`

```
\begin{table}[H]
    \caption{Prior sensitivity of each inference method per effect SD}
    \label{tab:prior_sensitivity}
    \begin{tabularx}{\textwidth}{lXXX}
    \midrule
    \multicolumn{1}{c}{Inference method} & \multicolumn{3}{c}{Prior sensitivity per effect SD}\\
    \cmidrule{2-4}
    \multicolumn{1}{c}{} & \multicolumn{1}{c}{0.2} & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.81}\\
    \midrule
    Savage-Dickey $BF_{10}$ & \centering `r ps_savage_dickey_bf_conv_0_2` & \centering `r ps_savage_dickey_bf_conv_0_51` & \centering `r ps_savage_dickey_bf_conv_0_81`\arraybackslash\\
    $dBF_{+-}$ & \centering `r ps_directional_bf_conv_0_2` & \centering `r ps_directional_bf_conv_0_51` & \centering `r ps_directional_bf_conv_0_81`\arraybackslash\\
    95\% HDI & \centering `r ps_hdi_conv_0_2` & \centering `r ps_hdi_conv_0_51` & \centering `r ps_hdi_conv_0_81`\arraybackslash\\
    P(effect > 0) & \centering `r ps_p_effect_conv_0_2` & \centering `r ps_p_effect_conv_0_51` & \centering `r ps_p_effect_conv_0_81`\arraybackslash\\
    \midrule
    \end{tabularx}
\end{table}
```







